An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/arch.tex
hyphens

Although the learner does necessarily rely on templates,
\app still offers a database to contain many templates,
as shown in Figure~\ref{fig-overview}.
Some of these templates are responsible for offering
specific system executional environment information.
It is widely known that any existing learning algorithm cannot
derive rules checking environment violation, \eg,
whether current account is the owner of a certain path.
In order to deal with comprehensive misconfiguration problems,
the learner needs a template DB to provide environment information,
thus detecting system environment related configuration errors.

>>>>

Although the learner does necessarily rely on templates,
\app still offers a database to contain many templates,
as shown in Figure~\ref{fig-overview}.
Some of these templates are responsible for offering
specific system executional environment information.
It is widely known that any existing learning algorithm cannot
derive rules checking environment violation, \eg,
whether current account is the owner of a certain path.
In order to deal with comprehensive misconfiguration problems,
the learner needs a template DB to provide environment information,
thus detecting system environment-related configuration errors.
